Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-10-21 doc/gaia-chapter.tex
more snippets in gaia-chapter

>>>>

\subsection{Examples of refinements}
Both libraries define constants like $0$, $1$, $\omega$, and arithmetic functions: successor, addition, multiplication, and exponential of base $\omega$ (function $\phi_0$). We prove consistency of these definitions. Finally, we prove that the boolean predicates `` to be in normal form'' are equivalent.

\subsubsection{A few constants}

\inputsnippets{T1Bridge/constantRefs}
